Hydra battles in Coq

### 2020-09-01 latex/chapter-large-sets.tex
minor corrections

Note that our decomposition of intervals works only if the intervals we consider are not empty. In order to ensure this property, we assume that $f\;k$ is always greater than $k$, which we note \texttt{S <= f}, or \texttt{(fun\_le S f)} (defined 
in~\href{../src/html/hydras.Prelude.Iterates.html\#fun_le}{Prelude.Iterates}).

@@

The functional \texttt{iterate}, similar to Standard Library's \texttt{Nat.iter},
is defined and studied in~\href{../src/html/hydras.Prelude.Iterates.html\#iterate}{Prelude.Iterates})

>>>>

Note that our decomposition of intervals works only if the intervals we consider are not empty. In order to ensure this property, we assume that $f\;k$ is always greater than $k$, which we note \texttt{S <<= f}, or \texttt{(fun\_le S f)} (defined 
in~\href{../src/html/hydras.Prelude.Iterates.html\#fun_le}{Prelude.Iterates}).

@@

The functional \texttt{iterate}, similar to Standard Library's \texttt{Nat.iter},
is defined and studied in~\href{../src/html/hydras.Prelude.Iterates.html\#iterate}{Prelude.Iterates}).

### 2020-09-01 latex/chapter-termination.tex
table of notations
corrections typo
minor corrections

@@

The following tactic tries to do a  transfinite induction on any ordinal \mathcolor{$\alpha<\epsilon_0$}.

@@

\begin{Coqsrc}
Lemma round_decr : forall h h', h -1-> h' -> m h' o< m h.
Proof.
   destruct 1 as [n H]; destruct H. 
   -  now apply R1_decr.
   -  now apply R2_decr with n.
Qed.
\end{Coqsrc}

@@

Let us recall three results we have proved so far.
\begin{itemize}
\item There exists a strictly decreasing variant which maps \texttt{Hydra} into 
the segment $[0,\epsilon_0)$ for proving the termination of any hydra battle
\item There exists \emph{no} such variant from \texttt{Hydra} into $[0,\omega^2)$ and
a fortiori into $[0,\omega)$.
\end{itemize}

>>>>

\label{sect:notation-phi0}

@@

The following tactic starts a proof by  transfinite induction on any ordinal \mathcolor{$\alpha<\epsilon_0$}.

@@

\begin{Coqsrc}
Lemma round_decr : forall h h', h -1-> h' -> m h' o< m h.
Proof.
   destruct 1 as [n [H | H]].
   -  now apply R1_decr.
   -  now apply R2_decr with n.
Qed.
\end{Coqsrc}

@@

Let us recall three results we have proved so far.
\begin{itemize}
\item There exists a strictly decreasing variant which maps \texttt{Hydra} into 
the segment $[0,\epsilon_0)$ for proving the termination of any hydra battle
\item There exists \emph{no} such variant from \texttt{Hydra} into 
$[0,\omega^2)$, \emph{a fortiori} into $[0,\omega)$.
\end{itemize}
